HTW Model

### 2024-02-22 Model/htw_model.qmd
add parameter comparisons between biggest differential subjects

@@

full_comparison |> filter(Fit_Method=="Test_Train") |> 
  ungroup() |>
  mutate(id = reorder(id, Error_difference)) %>%
  ggplot(aes(y=id,x=Error_difference,fill=Best_Model))+
  geom_col() +
  ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")+
  labs(fill="Best Model",x="Mean Model Error Difference (ALM - EXAM)",y="Participant")
```

>>>>

```{r}
#| fig-height: 8
#| fig-width: 12
#| 
vAlm <- c(29,70,68); cAlm <- c(73,49,128)

difAlm <-  post_dat_avg  |> filter(x==100,id %in% c(vAlm,cAlm), Fit_Method=="Test_Train") |>
    group_by(id, condit, Model, rank) %>%
      mutate(flab=paste0("Subject: ",id)) |>
    ggplot(aes(y=log(c), x = id,col=Model)) + 
  stat_pointinterval(position=position_dodge(.5)) +
   # ggh4x::facet_nested_wrap(condit~flab, axes = "all",scales="free_y",ncol=3) + 
      labs(title="c parameter - sbjs. with biggest diff. favoring ALM") +
  theme(legend.title = element_blank(), legend.position="right",plot.title=element_text(hjust=.4)) +ylim(c(-11,-4))

vAlm <- c(23,155,184); cAlm <- c(119,85,175)

difExam <- post_dat_avg  |> filter(x==100,id %in% c(vAlm,cAlm), Fit_Method=="Test_Train") |>
    group_by(id, condit, Model, rank) %>%
      mutate(flab=paste0("Subject: ",id)) |>
    ggplot(aes(y=log(c), x = id,col=Model)) + 
  stat_pointinterval(position=position_dodge(.1)) +
   # ggh4x::facet_nested_wrap(condit~flab, axes = "all",scales="free_y",ncol=3) + 
      labs(title="c parameter - sbjs. with biggest diff. favoring EXAM") +
  theme(legend.title = element_blank(), legend.position="right",plot.title=element_text(hjust=.4)) +ylim(c(-11,-4))

difAlm/difExam

vAlm <- c(29,70,68); cAlm <- c(73,49,128)

difAlm <-  post_dat_avg  |> filter(x==100,id %in% c(vAlm,cAlm), Fit_Method=="Test_Train") |>
    group_by(id, condit, Model, rank) %>%
      mutate(flab=paste0("Subject: ",id)) |>
    ggplot(aes(y=lr, x = id,col=Model)) + 
  stat_pointinterval(position=position_dodge(.5)) +
   # ggh4x::facet_nested_wrap(condit~flab, axes = "all",scales="free_y",ncol=3) + 
      labs(title="lr parameter - sbjs. with biggest diff. favoring ALM") +
  theme(legend.title = element_blank(), legend.position="right",plot.title=element_text(hjust=.4))+ylim(c(0,12))

vAlm <- c(23,155,184); cAlm <- c(119,85,175)

difExam <- post_dat_avg  |> filter(x==100,id %in% c(vAlm,cAlm), Fit_Method=="Test_Train") |>
    group_by(id, condit, Model, rank) %>%
      mutate(flab=paste0("Subject: ",id)) |>
    ggplot(aes(y=lr, x = id,col=Model)) + 
  stat_pointinterval(position=position_dodge(.1)) +
   # ggh4x::facet_nested_wrap(condit~flab, axes = "all",scales="free_y",ncol=3) + 
      labs(title="lr parameter - sbjs. with biggest diff. favoring EXAM") +
  theme(legend.title = element_blank(), legend.position="right",plot.title=element_text(hjust=.4)) +ylim(c(0,12))

difAlm/difExam
```

@@

full_comparison |> filter(Fit_Method=="Test_Train") |> 
  ungroup() |>
  mutate(id = reorder(id, Error_difference)) %>%
  ggplot(aes(y=id,x=Error_difference,fill=Best_Model))+
  geom_col() +
  ggh4x::facet_grid2(~condit,axes="all",scales="free_y", independent = "y")+
  labs(fill="Best Model",x="Mean Model Error Difference (ALM - EXAM)",y="Participant")

# full_comparison |> filter(Fit_Method=="Test_Train") |> 
#   ungroup() |>
#   mutate(id = reorder(id, Error_difference)) |>
#   left_join(post_dat_avg |> filter(x==100) |> select(-x) |> ungroup(), by=c("id","condit")) |>
#   ggplot(aes(y=id,x=c,fill=Best_Model))+
#   stat_pointinterval(position=position_dodge(.1))
